---
title: "Predictive Model for Fitness Exercise"
output: html_document
---

# Overview
This is Predictive model for fitness exercise in Practical machine learning course project of Data Science Specification(Couersera). 

This document is supported by R Markdown.

# Basic Setting
```{r}
# Load the data and library
if (! file.exists('./pml-training.csv')) {
        download.file('http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv', destfile = './pml-training.csv')
}
if (! file.exists('./pml-testing.csv')) {
        download.file('http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv', destfile = './pml-testing.csv')
}
train <- read.csv("pml-training.csv", header=TRUE, sep=",", na.strings=c("NA",""))
test <- read.csv("pml-testing.csv", header=TRUE, sep=",", na.strings=c("NA",""))
library(caret) ; library(randomForest);
set.seed(1432)
```

# Cleaning the data

```{r}
train <- train[,-1] 
inTrain = createDataPartition(train$classe, p=0.60, list=FALSE)
training = train[inTrain,]
testing = train[-inTrain,]
retain <- c((colSums(!is.na(training[,-ncol(training)])) >= 0.6*nrow(training)))
training   <-  training[,retain]
testing <- testing[,retain]
```

# Randomforest Modeling
Develop randomforest model, and show the result

```{r}
rfmodel <- randomForest(classe~., data=training, importance=TRUE)
rfmodel
conf_matrix<-confusionMatrix(predict(rfmodel,newdata=testing[,-ncol(testing)]),testing$classe)
conf_matrix
sum(diag(conf_matrix$table))/sum(conf_matrix$table)
```

Confusion Matrix achieved 99.95% accuracy. 
Out-Of-Sample Error Rate observed is 0.05%

# Predicting testdata & writing the result

```{r}
test <- test[,-1]
test <- test[ , retain]
test <- test[,-ncol(test)]
test <- rbind(training[100, -59] , test) 
predictions <- predict(rfmodel,newdata=test[-1,])
print(predictions)

write_files <- function(x) {
  n <- length(x)
  for (i in 1:n) {
    filename <- paste0("problem_id", i, ".txt")
    write.table(x[i], file=filename, quote=FALSE, row.names=FALSE,col.names=FALSE)
  }
}
write_files(predictions)
```

-fin-
