---
title: "Predictive Model for Fitness Exercise"
output: html_document
---

# Overview
This is Predictive model for fitness exercise in Practical machine learning course project of Data Science Specification(Couersera). 

This document is supported by R Markdown.

# Basic Setting
```{r}
# Load the data and library
if (! file.exists('./pml-training.csv')) {
        download.file('http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv', destfile = './pml-training.csv')
}
if (! file.exists('./pml-testing.csv')) {
        download.file('http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv', destfile = './pml-testing.csv')
}
training <- read.csv("pml-training.csv", header=TRUE)
testing <- read.csv("pml-testing.csv", header=TRUE)
library(caret) ; library(randomForest); library(plyr)
```

# Cleaning the data
Remove NA, unrelated col, and nearzero variances

```{r}
training <-training[,(colSums(is.na(training)) == 0)]
testing <- testing[,(colSums(is.na(testing)) == 0)]
col_removed <- c("X","user_name","raw_timestamp_part_1","raw_timestamp_part_2","cvtd_timestamp","new_window")
trainig <- training[,!(names(training) %in% col_removed)]
testing <- testing[,!(names(testing) %in% col_removed)]
nearzvar_training <- nearZeroVar(training, saveMetrics = TRUE)
nearzvar_testing <- nearZeroVar(testing, saveMetrics = TRUE)
training <- training[ , nearzvar_training$nzv==FALSE]
testing <- testing[ , nearzvar_testing$nzv==FALSE]
```

# Randomforest Modeling
Develop randomforest model, and show the result

```{r}
set.seed(1432)
inTrain = createDataPartition(training$classe, p = 0.75, list=FALSE)
traninig_train <- training[inTrain,]
training_test <- training[-inTrain,]
rfmodel <- randomForest(classe~., data=traninig_train, importance=TRUE)
rfmodel
```

# Randomforest Modeling
Develop randomforest model, and show the result

```{r}
set.seed(1432)
inTrain = createDataPartition(training$classe, p = 0.75, list=FALSE)
traninig_train <- training[inTrain,]
training_test <- training[-inTrain,]
rfmodel <- randomForest(classe~., data=traninig_train, importance=TRUE)
rfmodel
confusionMatrix(predict(rfmodel,newdata=training_test[,-ncol(training_test)]),training_test$classe)
```

Confusion Matrix achieved 100% accuracy. 
Out-Of-Sample Error Rate observed is 0.00%

# Predicting testdata

```{r}
pml_files = function(x){
        n = length(x)
        for(i in 1:n){
                filename = paste0("problem_id_",i,".txt") 
                write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
        }
}

predictionassignmet<- function(){
        prediction <- predict(rfmodel, testing)
        print(prediction)
        answers <- as.vector(prediction)
        pml_files(answers)
}
```

-fin-
